Make any stupid plot you want

### 2021-01-15 draft/sections/implementation.tex
scatter Q and nu, not sure I need data

@@

For the scatter plot in figure~\ref{fig:scatter}, we define $Q$ as 
 \begin{equation}
    Q(\mu_{xpos}, \mu_{ypos}, \mu_{facecolor}, \mu_{s})
 \end{equation}

@@

\begin{minted}{python}
    class Point(mcollections.Collection):
        # this is the visual fiber 
        required = {'x', 'y'}
        optional = {'facecolors', 's'} 
        def __init__(self, data, transforms, *args, **kwargs):
            """
            Parameters
            ----------
            data: sections of the fiber bundle
            transforms
            """
            super().__init__(*args, **kwargs)

            # check that the data you're trying to transform 
            # has a way to provide vertex data  
            assert 'vertex' in data.FB.K['tables']
            # check that you've given the required parameters
            utils.check_constraints(Point, transforms.keys())
            utils.validate_transforms(data.FB.F, transforms)

            self.data = data
            self.transforms = transforms

        def draw(self, renderer, *args, **kwargs):
            view = self.data.view('vertex') #resolve to size

            # call tau step
            visual = utils.convert_transforms(view, self.transforms)

            # assembles taus to generate idiom
            # dictionary here in place of visual(parameter) function

            visual['s'] = itertools.repeat(visual.get('s', 0.05))
            visual['facecolors'] = visual.get('facecolors', "C0")
            #switch out to a marker 
            self._paths = [mpath.Path.circle(center=(x,y), radius=s)  
                            for (x, y, s) 
                            in zip(visual['x'],visual['y'], visual['s'])]

            self.set_facecolors(visual['facecolors'])
            super().draw(renderer, *args, **kwargs)
    \end{minted}

>>>>

Because we do not expect the user to specify every visual parameter, we define a class of required visual variables that are intrinsic to S. %%need to revise for formality but
What I mean here is that you cannot construct the mark w/o this - position for scatter \& line, values for heatmap.

@@

For the scatter plot in figure~\ref{fig:scatter}, we define $Q$ as 
 \begin{equation}
    Q(\mu_{xpos}, \mu_{ypos}, \mu_{facecolor}, \mu_{s})
    \label{eq:scatter}
 \end{equation}

@@

\begin{minted}{python}
    class Point(mcollections.Collection):
        # this is the visual fiber 
        required = {'x', 'y'}
        optional = {'facecolors', 's'} 
        def __init__(self, data, transforms, *args, **kwargs):
            # check that the constraints on Q can be met  
        def draw(self, renderer, *args, **kwargs):
            # assemble the glyph
            super().draw(renderer, *args, **kwargs)
    \end{minted}

(subject to change). Unlike equation~\ref{eq:scatter}, we pass also pass a reference to the data so that getting the data can be fully curried until absolutely necessary. The \texttt{*args} and \texttt{**kwargs} are artifacts of using Matplotlib as a base. We pass in the $\mu$ as the dictionary "transforms" mostly for readability, which is also why we define the visual fiber as class attributes.

Inside the \texttt{__init__} constructor, is a check if there is a valid mapping between $S$ and $K$.  Line 7-8 check if the user has passed in the required $\mu$ and whether the $\nu$ functions are valid for the input data.

\begin{minted}[lineno]{python}
def __init__(self, data, transforms, *args, **kwargs):
    super().__init__(*args, **kwargs)
    # check that the data you're trying to transform 
    # has a way to provide vertex data  
    assert 'vertex' in data.FB.K['tables']
    # check that you've given the required parameters
    utils.check_constraints(Point, transforms.keys())
    utils.validate_transforms(data.FB.F, transforms)

    self.data = data
    self.transforms = transforms
\end{minted}

Lines 9-10 attach the data and transforms to the $Point$ object as a concession to the Matplotlib architecture that seperates drawing from creation. In \texttt{draw}, the attributes of the graphic are set to the different sections of the visual fiber bundle.

\begin{minted}[lineno]{python}
def draw(self, renderer, *args, **kwargs):
    view = self.data.view('vertex') #resolve to size

    # \nu(\tau)
    visual = utils.convert_transforms(view, self.transforms)

    # assembles taus to generate idiom
    visual['s'] = itertools.repeat(visual.get('s', 0.05))
    visual['facecolors'] = visual.get('facecolors', "C0")
    #switch out to a marker 
    self._paths = [mpath.Path.circle(center=(x,y), radius=s)  
                    for (x, y, s) 
                    in zip(visual['x'],visual['y'], visual['s'])]

    self.set_facecolors(visual['facecolors'])
    super().draw(renderer, *args, **kwargs)
\end{minted}
Line 1 pulls back into the data bundle and returns $\tau = \{\tau_0, \ldots, tau_{n}\}$. Line 3 applies the transforms $\nu$ to $\tau$ to build the visual bundle $V$.  Line 8 sets the abstract segment marks with the visual characteristics. Line 10 passes this information to the renderer, acting like a $rho$.

The visual fiber bundle is specified as a dictionary $\{\mbox{parameter}: (\mbox{variable}, \nu), \mbox{parameter}:\mbox{value}\}$ 
\begin{minted}[lineno]{python}

transforms = {'y': ('v2', position.Identity()),       
              'x': ('v4', position.Identity()),
              'facecolors': ('v3', color.Categorical( {'true':'deeppink', 'false':'deepskyblue'})), 
              's':.01}
\end{minted}

where the $\nu$ functions are represented as classes so that parameters can be curried. For example, \texttt{color.Categorical} is a whole set of $\nu$ functions explicitly tuned to specific categorical mappings. A pure functional approach would mean the user would have to write new functions

\begin{minted}[lineno]{python}
def color_true_deepink_false_deepink(value):
    return {'true':'deeppink', 'false':'deepskyblue'}[value]

\end{minted}

for every categorical colormapping, which would be somewhat untenable. An alternative approach could be to partially curry:

\begin{minted}[lineno]{python}
     'facecolors': ('v3', (color.categorical, {'true':'deeppink', 'false':'deepskyblue'}))
\end{minted}

but that doesn't allow for as easy reuse? (I should probably actually just switch to this form) The \textt{color.categorical} function is implemented as 
\begin{minted}[lineno]{python}
class Categorical:
    def __init__(self, mapping):
        """goal of init is to store parameters that would otherwise be
        curried higher level function"""
        assert(mcolors.is_color_like(color) for color in mapping.values())
        self._mapping = mapping

    def convert(self, value):
        values = np.atleast_1d(np.array(value, dtype=object))
        return [mcolors.to_rgba(self._mapping[v]) for v in values]

    def validate(self, mtype):
        return mtype in ['nominal']
\end{minted}

where the \texttt{convert} function converts the input value to the internal normalized form Matplotlib expects. The `\texttt{validate}' function checks which monoid actions the transform supports; optimally this method should be replaced by functions that check the properties, for example a \texttt{is_ordinal} method that checks that monotonicity is preserved.

#does the data even matter?
